Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/approach.tex
updated lots of text

Our training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarities are then computed for the data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.

>>>>

Our training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
Each comment is assessed by three different people independently.
For each \texttt{YES} vote, a single point is given to that comment.
This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.

The similarity and dissimilarity metrics are then computed for the data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.

### 2014-07-28 sections/discussion.tex
updated lots of text

% noisy data, and binary classification
Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear.
These samples cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

% tuning the F score for precision and recall
Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
For instance, if we wanted to measure the amount of useful comments within a large dataset, we can give more weight to precision, sacrificing some good comments.
If we wanted to modify a code review software such that it displays useful comments more prominently, we can give more weight to recall.
%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful
During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

@@

By removing the samples with scores of 1 and 2 from our data set, leaving with 209 samples without disagreements, we can perform a binary classification, in which all comments will receive either a positive or negative score.
By cross-validation using only samples in total agreement, we obtained a much better F$_1$ score of 0.896.

@@

\begin{figure}[h]
\centering
\includegraphics[width=3in]{binary}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}

>>>>

% noisy data, and binary classification
Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

% tuning the F score for precision and recall
Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
For instance, if we wanted to measure the amount of useful comments within a large dataset, more weight can be given to precision, sacrificing some useful comments.
If we wanted to modify a code review software such that it displays useful comments more prominently, more weight can be given to recall.

%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful
During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

@@

Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear on undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.

@@

\begin{figure}[h]
\centering
\includegraphics[width=3in]{posneg}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}
